### 2019-08-07 paper-body.tex
Added: Description of collision error experiments, including graph for central, control version

\section{Correctness Experiments}
\section{Case Study: Suspension Bridge}

>>>>

\section{Correctness Experiments}
In the following section we explore the correctness of collisions between objects, i.e. do objects have the same collision behaviour in a AP as they do in a centralised system. We are concerned with objects that are migrating and/or interacting with an object that has recently migrated.
We will now explain how a naive system can lead to erroneous collision behaviour and AP can lead to erroneous collision behaviour if speed, frame-time or latency go above the user-defined tolerances.

Erroneous collisions fall into two categories:
\begin{itemize}
	\item Missed collisions, collisions that should have taken place but were not detected by the physics engine e.g. Bullet through paper problem.
	\item Late collisions, collisions that were detected later than they should have been and result in not only different collision results, but also unstable collision response.
\end{itemize}

%TODO: Expand on late collisions producing different results?

To understand how late collisions lead to unstable collision response, we must first understand how in real-time collision detection works. In real-time physics engines, objects move in descrete steps, as a result of this, when two objects collide, they overlap each other i.e. penetrate. The collision is resolved by calculating the forces resulting from the collision and moving the objects so they no longer overlap (in PhysX if penetration is high, the latter may be done over several physics time-steps). If the penetration is high, such as in the case of a late collision response or if two objects are moving at high speed towards one another, the collision response can no longer guarantee stable results.

It is possible to detect late collisions between objects. Given the relative speed of the two objects and the physics time-step, it possible to calculate the maximum expected penetration distance. If a collision is detected and it is above this value, it means it is a late collision.

Maximum penetration for a given speed occurs when two objects travelling directly towards each other have, in the final time-step before colliding the two objects have no distance between them, but are not overlapping, so not colliding. The next physics time-step, the collision will be detected and will have the maximum penetration possible for that relative speed. Re-arranging s=d/t, to d=s.t and substituting the physics time-step for t, gives us the maximum distance (penetration) for a relative speed, and we are able to plot the maximum expected penetration line.

%In real-time physics, speed of calculation is favoured over accuracy of collision response, as a result of this

%, this is known as the collision response (in real-time physics, speed of calculation is favoured over accuracy of collision response). High collision penetration e.g. if two objects are moving quickly towards one another, can lead to unstable collision response, which is undesirable.

%TODO: cite that deep penetration is bad

Experiments were carried out where collision results were recorded and used to detect missed and late collisions of objects. The experiment scenario used only two objects, meaning if there was a missed collision there would be no collision output. The two objects start the scenario with a specified velocity (drag and gravity are disabled), the direction being directly towards the other object and the two objects were given the same speed, which is varied throughout the experiment. Spheres were used, so rotational effects don't need to be accounted for.

A control experiment on a centralised system was performed, in which the scenario was repeated multiple times. The purpose of this experiment was to confirm the predicted maximum expected penetration. Fig. \ref{fig_ErrorCentral} shows the penetration of objects with increasing speed in a centralised simulation and demonstrates that penetration is never greater than the maximum expected penetration.

% TODO: Add number of collisions and number of missed collisions
\begin{figure}[!t]
	\centering
	\includegraphics[width=\textwidth]{errorGraphCentral}
	\caption{Penetration of objects with increasing speed and maximum expected penetration}
	\label{fig_ErrorCentral}
\end{figure}

AP can only lead to late or missed collisions when at least one object involved in the collision has just migrated (received since the last physics time-step). In order to test this case, the same scenario as the control was used with two servers. The two spheres were given starting positions so the two would collide at a point on the boundary between servers, thus creating the most likely situation for objects collide with each other in their first time-step after being migrated. The purpose of this experiment is to demonstrate that collisions in AP are always correct if the respective values remain within their tolerances.
Only objects that have just migrated are considered in the experiment results. The two servers use the same tolerances used in the performance experiments, including a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$.

%TODO: Graph for 2-server collisions. Will need set values with tolerances to max and vary them one at a time.

%TODO: Missed collisions (and number of, mean and max error)

\section{Case Study: Suspension Bridge}
